VM-Centric Snapshot Deduplication for Cloud Data Backup

### 2015-03-07 snapshot_system/mass.tex
re

\documentclass[10pt,reprint]{socc14}
\usepackage{mathptmx}
\usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
\usepackage{subfigure}
\usepackage{epsfig}
\usepackage{multirow}
\usepackage{array}
\usepackage{breqn}
\usepackage{tikz}
\usetikzlibrary{calc,shapes,positioning,decorations.pathmorphing}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{sansmath}
\usepackage{booktabs}
\usepackage{soul}
\pgfplotsset{compat=1.5}
\DeclareGraphicsExtensions{.pdf}

@@

%\linespread{.98} % to squeeeze lines and put figures in same page
\begin{document}
\special{papersize=8.5in,11in}
\setlength{\pdfpageheight}{\paperheight}
\setlength{\pdfpagewidth}{\paperwidth}
\conferenceinfo{Submission to SoCC '14}{October, 2014, Seattle, WA, USA}
\copyrightyear{2014}
\copyrightdata{978-1-nnnn-nnnn-n/yy/mm}
\doi{nnnnnnn.nnnnnnn}
%\title{VM-Centric Deduplication with Fault Isolation for Virtual Machine Snapshot Backup }
%Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud}

%with Fault Isolation 
\title{VM-Centric Snapshot Deduplication for Cloud Data Backup}
%VM-Centric  Deduplication  with Fault Isolation for Snapshot Backup in the Cloud
\comments{
\authorinfo{Wei Zhang\and Daniel Agun\and Tao Yang}
           {UC Santa Barbara}
           {\{wei,dagun,tyang\}@cs.ucsb.edu}
\authorinfo{Hong Tang}
           {Alibaba Inc.}
           {hongtang@alibaba-inc.com}
\authorinfo{Rich Wolski}
           {UC Santa Barbara}
           {rich@cs.ucsb.edu}
}
 \authorinfo{
   Wei Zhang$^{\ast}$, Daniel Agun$^\star$, Tao Yang$^\star$, Rich Wolski$^{\star}$, and  
Hong Tang$^\dagger$\\
   $^\star$University of California at Santa Barbara \ \ \  \\
   $^\ast$Pure Storage Inc.\ \ \  $^\dagger$Alibaba Inc. }
%  \{wei, dagun,tyang,rich\}@cs.ucsb.edu, hongtang@alibaba-inc.com

@@

\maketitle

@@

\category{}{Information Systems}{Information Storage Systems}
\category{}{Distributed Architectures}{Cloud Computing}
%\category{D.2.8}{Information Systems}{Information Storage Systems}
\terms{Design, Experimentation, Performance}

\keywords
Virtual machine images, snapshot backup and deletion, source-side deduplication, cluster-based architectures

>>>>

\documentclass[10pt,reprint]{socc14}

%\documentclass[conference]{IEEEtran}

\usepackage{mathptmx}
\usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
\usepackage{subfigure}
\usepackage{epsfig}
\usepackage{multirow}
\usepackage{array}
\usepackage{breqn}
\usepackage{tikz}
\usetikzlibrary{calc,shapes,positioning,decorations.pathmorphing}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{sansmath}
\usepackage{booktabs}
\usepackage{soul}
\pgfplotsset{compat=1.5}
\DeclareGraphicsExtensions{.pdf}

@@

%\linespread{.98} % to squeeeze lines and put figures in same page
\begin{document}
\special{papersize=8.5in,11in}
\setlength{\pdfpageheight}{\paperheight}
\setlength{\pdfpagewidth}{\paperwidth}
%\conferenceinfo{Submission to SoCC '14}{October, 2014, Seattle, WA, USA}
%\copyrightyear{2014}
%\copyrightdata{978-1-nnnn-nnnn-n/yy/mm}
%\doi{nnnnnnn.nnnnnnn}
%\title{VM-Centric Deduplication with Fault Isolation for Virtual Machine Snapshot Backup }
%Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud}

%with Fault Isolation 
\title{VM-Centric Snapshot Deduplication for Cloud Data Backup}
%VM-Centric  Deduplication  with Fault Isolation for Snapshot Backup in the Cloud
\comments{
\authorinfo{Wei Zhang\and Daniel Agun\and Tao Yang}
           {UC Santa Barbara}
           {\{wei,dagun,tyang\}@cs.ucsb.edu}
\authorinfo{Hong Tang}
           {Alibaba Inc.}
           {hongtang@alibaba-inc.com}
\authorinfo{Rich Wolski}
           {UC Santa Barbara}
           {rich@cs.ucsb.edu}
}

 \authorinfo{
   Wei Zhang$^{\star,\ast}$, Daniel Agun$^\star$, Tao Yang$^\star$, Rich Wolski$^{\star}$, and  
Hong Tang$^\dagger$\\
   $^\star$University of California at Santa Barbara \ \ \  \\
   $^\ast$Pure Storage Inc.\ \ \  $^\dagger$Alibaba Inc. }
%  \{wei, dagun,tyang,rich\}@cs.ucsb.edu, hongtang@alibaba-inc.com

@@

\comments{
\author{
\IEEEauthorblockN{Wei Zhang\IEEEauthorrefmark{1,2}, Daniel Agun\IEEEauthorrefmark{2}, 
Tao Yang\IEEEauthorrefmark{1}, Rich Wolski\IEEEauthorrefmark{1}, 
Hong Tan\IEEEauthorrefmark{3}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}University of California at Santa Barbara}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Pure Storage Inc.}
\IEEEauthorblockA{\IEEEauthorrefmark{3}Alibaba Inc.}
%Wei Zhang$^{\star\dagger}$, Hong Tang$^\dagger$, Hao Jiang$^\dagger$, Tao Yang$^\star$,
%Xiaogang Li$^\dagger$, and Rachael Zeng$^\dagger$ \\
%   {\normalsize $^\star$UC Santa Barbara}\\
%   {\normalsize$^\dagger$Alibaba.com}
}
}
\maketitle

@@

%\category{}{Information Systems}{Information Storage Systems}
%\category{}{Distributed Architectures}{Cloud Computing}
%\category{D.2.8}{Information Systems}{Information Storage Systems}
%\terms{Design, Experimentation, Performance}

%\keywords
%Virtual machine images, snapshot backup and deletion, source-side deduplication, cluster-based architectures
